\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-09-05 RA-L/experiment.tex
Fixed a conflict.
fixed another conflict,,,
Worked on intro

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiment}\label{sec:expResults}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[!htb]
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{
\begin{overpic}[width =\figwid]{twoR1.pdf}\put(12,70){$t$  = 0 s}\end{overpic}
\begin{overpic}[width =\figwid]{twoR2.pdf}\put(12,70){$t$  = 60 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR3.pdf}\put(12,70){$t$  = 150 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR4.pdf}\put(12,70){$t$  = 160 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR5.pdf}\put(12,70){$t$  = 210 s}
\end{overpic}}
\vspace{-3em}
\caption{\label{fig:storyReal}{
Position control of two kilobots (Alg. \ref{alg:XControl}) steered to corresponding colored circle. Boundary walls have nearly infinite friction, so the green robot is stopped by the wall from $t = 60$s until the commanded input is directed away form the wall at $t=150$s, while the pink robot in free-space is unhindered.}
%\vspace{-1em}
}
\end{figure*}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:setup}
Hardware platform:  table with 1$\times$1 m workspace, surrounded by eight remotely triggered LED floodlights, with an overhead machine vision system.
}
\vspace{-1em}
\end{figure}
\subsection{Hardware Experiment: Position Control of Two Robots}
The walls of the hardware platform have almost infinite friction, due to a laser-cut, zigzag border and the three-legged design of the kilobots. When a kilobot is steered into the zigzag border, they pin themselves to the wall unless the global input directs them away from the wall.  This wall friction is sufficient to enable independent control of two kilobots, as shown in Fig.~\ref{fig:storyReal}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{experiment}\label{sec:expResults}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[!htb]
\centering
\renewcommand{\figwid}{0.38\columnwidth}
{
\begin{overpic}[width =\figwid]{twoR1.pdf}%\put(12,70){$t$  = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR2.pdf}\put(12,70){$t$  = 60 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR3.pdf}\put(12,70){$t$  = 150 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR4.pdf}\put(12,70){$t$  = 160 s}
\end{overpic}
\begin{overpic}[width =\figwid]{twoR5.pdf}\put(12,70){$t$  = 210 s}
\end{overpic}}
%\vspace{-3em}
\caption{\label{fig:storyReal}Position control of two kilobots (Alg. \ref{alg:XControl}) steered to corresponding colored circle. Boundary walls have nearly infinite friction, so the green robot is stopped by the wall from $t = 60$s until the commanded input is directed away form the wall at $t=150$s, while the pink robot in free-space is unhindered.}
\end{figure*}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{SetUp.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:setup}
Hardware platform:  table with 1$\times$1 m workspace, surrounded by eight  triggered LED floodlights, with an overhead machine vision system.
}
\vspace{-1em}
\end{figure}
\subsection{Hardware Experiment: Position Control of Two Robots}
The walls of the hardware platform have almost infinite friction, due to a laser-cut, zigzag border and the three-legged design of the kilobots. When a kilobot is steered into the zigzag border, they pin themselves to the wall unless the global input directs them away from the wall.  This wall friction is sufficient to enable independent control of two kilobots, as shown in Fig.~\ref{fig:storyReal}.

### 2016-09-05 RA-L/intro.tex
Worked on intro

%One surprising result was that humans that only knew the swarm's mean and covariance completed the task faster that humans who knew the position of every robot~\cite{Becker2013b}. Our previous work focused on a block-pushing task, where a swarm of robots pushed a larger block through a 2D maze. 
Even without obstacles or boundaries, the mean position of the swarm in \eqref{eq:swarmDynamics} is controllable.  By adding rectangular boundary walls, some higher-order moments such as the swarm's position variance orthogonal to the boundary walls ($\sigma_x$ and $\sigma_y$ for a workspace with axis-aligned walls) are also controllable. 
%The usefulness of these techniques was recently demonstrated by several automatic controllers. One controller steered a swarm of robots to push a larger block through a 2D maze~\citet{ShahrokhiIROS2015}. 
A limitation is that global control can only compress a swarm orthogonal to obstacles.  However, navigating through narrow passages often requires control of the variance and the covariance.
%This means the swarm could not navigate workspaces with narrow corridors with other orientations, such as those shown in Fig.\ \ref{fig:covFriction}.
%Challenges like these require a controller that regulates the swarm's position covariance, $\sigma_{xy}$.

This paper provides analytical position control results in two canonical workspaces with frictionless walls \S\ref{subsec:FluidInTank}.  These results are limited in the set of shapes that can be generated.  To extend the range of possible shapes, we introduce wall friction to the system model \S \ref{subsec:WallFriction}.  We prove that two orthogonal boundaries with high friction are sufficient to arbitrarily position two robots \S \ref{sec:PostionControl2Robots}, and extend this to prove a rectangular workspace with high friction boundaries is sufficient to position a swarm of $n$ robots arbitrarily within a subset of the workspace \S \ref{sec:PostionControlnRobots}.
\S \ref{sec:simulation} describes implementations of both position control algorithms in simulation and  \S \ref{sec:expResults} describes experiments with a hardware setup and up to 100 robots, as shown in Fig.~\ref{fig:IntroPic}. After a review of recent related work \S \ref{sec:RelatedWork}, we end with directions for future research \S \ref{sec:conclusion}.
%For controlling $\sigma_{xy}$, we prove that the swarm position covariance $\sigma_{xy}$ is controllable given boundaries with non-zero friction. 
%We then prove that two orthogonal boundaries with high friction are sufficient to arbitrarily position a swarm of $n$ robots. 
%We conclude by designing controllers that efficiently regulate $\sigma_{xy}$.
%This paper
%(1) proves that the swarm position covariance $\sigma_{xy}$ is controllable given boundaries with non-zero friction,  %where do we do this?
%(2) proves that two orthogonal boundaries with high friction are sufficient to arbitrarily position two robots, 
%(3) proves that two orthogonal boundaries with high friction are sufficient to arbitrarily position a swarm of $n$ robots, 
%(4) shows full-state position control with 2 or more robots using  extensive simulations, and
%(5) demonstrate covariance control on our hardware platform with a large number of hardware robots.
%TODO JOURNAL: design controllers that efficiently regulate $\sigma_{xy}$.
%TODO JOURNAL: We will design Lyapunov-inspired controllers for $\sigma_{xy}$ to prove controllability. 
%TODO JOURNAL:  and rank controllability as a function of friction.
% TODO: JOURNAL: and vary wall friction by laser-cutting boundary walls with a variety of profiles. 
%\begin{figure}[t]
%\centering
%\begin{overpic}[width = \columnwidth]{Covariance.jpg}\end{overpic}
%\vspace{-1em}
%\caption{\label{fig:covFriction} Maintaining group cohesion while steering a swarm through an arbitrary maze requires covariance control.
%}\vspace{-1em}
%\end{figure}
% Our paper is organized as follows.  After a discussion of related work in Section \ref{sec:RelatedWork}, we describe our experimental methods for an online human-user experiment in Section \ref{sec:expMethods}.  We report the results of our experiments in Section \ref{sec:expResults}, discuss the lessons learned in Section \ref{sec:discussion}, and end with concluding remarks in Section \ref{sec:conclusion}.

>>>>

%One surprising result was that humans that only knew the swarm's mean and covariance completed the task faster that humans who knew the position of every robot~\cite{Becker2013b}. Our previous work focused on a block-pushing task, where a swarm of robots pushed a larger block through a 2D maze. 
Even without obstacles or boundaries, the mean position of the swarm in \eqref{eq:swarmDynamics} is controllable.  By adding rectangular boundary walls, some higher-order moments such as the swarm's position variance orthogonal to the boundary walls ($\sigma_x$ and $\sigma_y$ for a workspace with axis-aligned walls) are also controllable~\citep{ShahrokhiIROS2015}. 
%The usefulness of these techniques was recently demonstrated by several automatic controllers. One controller steered a swarm of robots to push a larger block through a 2D maze~\citet{ShahrokhiIROS2015}. 
A limitation is that global control can only compress a swarm orthogonal to obstacles.  However, navigating through narrow passages often requires control of the variance and the covariance.
%This means the swarm could not navigate workspaces with narrow corridors with other orientations, such as those shown in Fig.\ \ref{fig:covFriction}.
%Challenges like these require a controller that regulates the swarm's position covariance, $\sigma_{xy}$.

\S\ref{subsec:FluidInTank} provides analytical position control results in two canonical workspaces with frictionless walls.  These results are limited in the set of shapes that can be generated.  To extend the range of possible shapes, \S \ref{subsec:WallFriction} introduces wall friction to the system model.  We prove that two orthogonal boundaries with high friction are sufficient to arbitrarily position two robots in \S \ref{sec:PostionControl2Robots}, and \S \ref{sec:PostionControlnRobots} extends this to prove a rectangular workspace with high-friction boundaries can position a swarm of $n$ robots arbitrarily within a subset of the workspace.
\S \ref{sec:simulation} describes implementations of both position control algorithms in simulation and  \S \ref{sec:expResults} describes experiments with a hardware setup and up to 100 robots, as shown in Fig.~\ref{fig:IntroPic}. After a review of recent related work \S \ref{sec:RelatedWork}, we end with directions for future research \S \ref{sec:conclusion}.
%For controlling $\sigma_{xy}$, we prove that the swarm position covariance $\sigma_{xy}$ is controllable given boundaries with non-zero friction. 
%We then prove that two orthogonal boundaries with high friction are sufficient to arbitrarily position a swarm of $n$ robots. 
%We conclude by designing controllers that efficiently regulate $\sigma_{xy}$.
%This paper
%(1) proves that the swarm position covariance $\sigma_{xy}$ is controllable given boundaries with non-zero friction,  %where do we do this?
%(2) proves that two orthogonal boundaries with high friction are sufficient to arbitrarily position two robots, 
%(3) proves that two orthogonal boundaries with high friction are sufficient to arbitrarily position a swarm of $n$ robots, 
%(4) shows full-state position control with 2 or more robots using  extensive simulations, and
%(5) demonstrate covariance control on our hardware platform with a large number of hardware robots.
%TODO JOURNAL: design controllers that efficiently regulate $\sigma_{xy}$.
%TODO JOURNAL: We will design Lyapunov-inspired controllers for $\sigma_{xy}$ to prove controllability. 
%TODO JOURNAL:  and rank controllability as a function of friction.
% TODO: JOURNAL: and vary wall friction by laser-cutting boundary walls with a variety of profiles. 
%\begin{figure}[t]
%\centering
%\begin{overpic}[width = \columnwidth]{Covariance.jpg}\end{overpic}
%\vspace{-1em}
%\caption{\label{fig:covFriction} Maintaining group cohesion while steering a swarm through an arbitrary maze requires covariance control.
%}\vspace{-1em}
%\end{figure}
% Our paper is organized as follows.  After a discussion of related work in Section \ref{sec:RelatedWork}, we describe our experimental methods for an online human-user experiment in Section \ref{sec:expMethods}.  We report the results of our experiments in Section \ref{sec:expResults}, discuss the lessons learned in Section \ref{sec:discussion}, and end with concluding remarks in Section \ref{sec:conclusion}.

### 2016-09-05 RA-L/theory.tex
Worked on intro

Computing the means, variances, covariance, and correlation requires integrating over the region $R$ containing the swarm:  %This is simplified using an indicator function $\bm{1}_A(x,y)$ that returns 1 if inside the region containing the swarm, and 0 else. 
%The formulas for means $(\bar{x},\bar{y})$, covariance $(\sigma^2_x,\sigma^2_y,\sigma_{xy})$, and correlation $\rho_{xy}$ are as follows: %, integrated over the unit square with $x$ and $y$ from 0 to 1:

\begin{align}
\bar{x} &=\frac{\iint_R x \,dx\,dy}{A} \label{eq:meanInSquareWorkspace}
\text{, }\qquad \bar{y}=\frac{\iint_R y \,dx\,dy}{A}
\end{align}
\begin{align}
\sigma^2_x &=\frac{\iint_R \left(x-\bar{x}\right)^2  \,dx \,dy}{A}  \label{eq:varInSquareWorkspace}
\text{, } \sigma^2_y =\frac{\iint_R  \left(y-\bar{y}\right)^2 \,dx \,dy}{A}
\end{align}
\begin{align}
\sigma_{xy} &= \frac{\iint_R  \left(x-\bar{x}_x\right) \left(y-\bar{y}\right) \, dx \,dy}{A} \label{eq:covAndcorrInSquareWorkspace}
\text{, }\rho_{xy} = \frac{\sigma^2_x}{\sigma_x\sigma_y}
\end{align}

@@

\begin{align}
F_{\text{\emph{forward}}} &=  F \sin(\theta) - F_f  \nonumber \\
\text{where }  F_f &= \begin{cases}  \mu_f N, &  \mu_f N < F \sin(\theta)  \label{eq:frictionmodel}  \\
F \sin(\theta), & \text{else} \end{cases} \\ %\sign(F \sin(\theta) ) \cdot  \max(0, | F sin\theta |- |F_f|)
\text{and } N &= F \cos(\theta) \nonumber
\end{align}
 Fig.~\ref{fig:friction} shows the resultant forces on two robots when one is touching a wall. As illustrated, both experiences different net forces although each receives the same inputs.
  For ease of analysis, the following algorithms assume $\mu_f$ is infinite and robots touching the wall are prevented from sliding along the wall.
This means that if one robot is touching the wall and another robot is free, if the control input is parallel or into the wall, the touching robot will not move. 
The next section shows how a system with friction model \eqref{eq:frictionmodel} and two orthogonal walls are sufficient to arbitrarily position two robots. 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\columnwidth]{friction.pdf} 
\vspace{-1em}
\caption{Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a robot near a wall, but not for a free robot. At left there is a fluid and inside it the velocity of the robot is almost zero at the surface and is more and more until it is the same as the free space on the threshold.}
\label{fig:friction}
\end{center}
\end{figure}

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of $2$ Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{\begin{overpic}[width =\figwid]{S1_1.png}\put(55,15){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_2.png}\put(55,15){$t$ = 0.14 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_3.png}\put(55,15){$t$  = 0.29 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_4.png}\put(55,15){$t$  = 0.45 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_5.png}\put(55,15){$t$  = 0.7 s}
\end{overpic}}\\
%{\begin{overpic}[width =\figwid]{two_1.jpg}\put(45,75){$t$  = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_2.jpg}\put(45,75){$t$  = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}\\
%\vspace{.5em}
%{\begin{overpic}[width =\figwid]{S3_1.jpg}\put(45,75){$t$ = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_2.jpg}\put(45,75){$t$ = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}
%\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. The algorithm only requires friction along the bottom and left walls.
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  The path given by  Alg.\ \ref{alg:PosControl2Robots} is shown with solid arrows.
%The bottom row shows an extreme case where the robots must switch position.
}
%\vspace{-2em}
}
\end{figure*}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{driftmove.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:driftmove}
A  $\operatorname{DriftMove}(\alpha, \beta, \epsilon)$ to the right consists of repeating a triangular movement sequence $\{ (\beta/2,-\epsilon),(\beta/2,\epsilon),(-\alpha,0)\}$. The robot $A$ touching a top wall will move right $\beta$ units, while robots not touching the top move right $\beta-\alpha$.
}
\end{figure}
\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{PositionNrobots.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:construction2d}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, $n$ robot position control  using wall friction.
}
\end{figure}

>>>>

Computing means, variances, covariance, and correlation requires integrating over the region $R$ containing the swarm:  %This is simplified using an indicator function $\bm{1}_A(x,y)$ that returns 1 if inside the region containing the swarm, and 0 else. 
%The formulas for means $(\bar{x},\bar{y})$, covariance $(\sigma^2_x,\sigma^2_y,\sigma_{xy})$, and correlation $\rho_{xy}$ are as follows: %, integrated over the unit square with $x$ and $y$ from 0 to 1:

\begin{align}
\bar{x} &=\frac{\iint_R x \,dx\,dy}{A} \label{eq:meanInSquareWorkspace}
\text{, }\qquad \bar{y}=\frac{\iint_R y \,dx\,dy}{A} \\
%\end{align}
%\begin{align}
\sigma^2_x &=\frac{\iint_R \left(x-\bar{x}\right)^2  \,dx \,dy}{A}  \label{eq:varInSquareWorkspace}
\text{, } \sigma^2_y =\frac{\iint_R  \left(y-\bar{y}\right)^2 \,dx \,dy}{A}\\
%\end{align}
%\begin{align}
\sigma_{xy} &= \frac{\iint_R  \left(x-\bar{x}_x\right) \left(y-\bar{y}\right) \, dx \,dy}{A} \label{eq:covAndcorrInSquareWorkspace}
\text{, }\rho_{xy} = \frac{\sigma^2_x}{\sigma_x\sigma_y}
\end{align}

@@

\begin{align}
F_{\text{\emph{forward}}} &=  F \sin(\theta) - F_f  \nonumber \\
\text{where }  F_f &= \begin{cases}  \mu_f N, &  \mu_f N < F \sin(\theta)  \label{eq:frictionmodel}  \\
F \sin(\theta), & \text{else} \end{cases} \\ %\sign(F \sin(\theta) ) \cdot  \max(0, | F sin\theta |- |F_f|)
\text{and } N &= F \cos(\theta) \nonumber
\end{align}
 Fig.~\ref{fig:friction} shows the resultant forces on two robots when one is touching a wall. As illustrated, both experiences different net forces although each receives the same inputs.
  For ease of analysis, the following algorithms assume $\mu_f$ is infinite and robots touching the wall are prevented from sliding along the wall.
This means that if one robot is touching the wall and another robot is free, if the control input is parallel or into the wall, the touching robot will not move. 
The next section shows how a system with friction model \eqref{eq:frictionmodel} and two orthogonal walls are sufficient to arbitrarily position two robots. 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\columnwidth]{friction.pdf} 
\vspace{-1em}
\caption{Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a robot near a wall, but not for a free robot. (Right) velocity of a fluid reduces to zero at the boundary.}
\label{fig:friction}
\end{center}
\end{figure}

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of $2$ Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{\begin{overpic}[width =\figwid]{S1_1.png}\put(55,15){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_2.png}\put(55,15){$t$ = 0.14 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_3.png}\put(55,15){$t$  = 0.29 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_4.png}\put(55,15){$t$  = 0.45 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_5.png}\put(55,15){$t$  = 0.7 s}
\end{overpic}}\\
%{\begin{overpic}[width =\figwid]{two_1.jpg}\put(45,75){$t$  = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_2.jpg}\put(45,75){$t$  = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}\\
%\vspace{.5em}
%{\begin{overpic}[width =\figwid]{S3_1.jpg}\put(45,75){$t$ = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_2.jpg}\put(45,75){$t$ = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}
%\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. The algorithm only requires friction along the bottom and left walls.
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  Solid arrows show path given by  Alg.\ \ref{alg:PosControl2Robots}.
Online demonstration and source code at \citet{Shahrokhi2015mathematicaParticle}.
%The bottom row shows an extreme case where the robots must switch position.
}
%\vspace{-2em}
}
\end{figure*}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=.9\columnwidth]{driftmove.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:driftmove}
A  $\operatorname{DriftMove}(\alpha, \beta, \epsilon)$ to the right repeats a triangular movement sequence $\{ (\beta/2,-\epsilon),(\beta/2,\epsilon),(-\alpha,0)\}$. Robot $A$ touching a top wall moves right $\beta$ units, while robots not touching the top move right $\beta-\alpha$.
}
\end{figure}
\begin{figure}
\begin{center}
	\includegraphics[width=1.0\columnwidth]{multirobotSliderHardware.pdf}
\end{center}
\vspace{-1em}
\caption{\label{fig:construction2d}
Illustration of Alg.\ \ref{alg:PosControlNRobots}, $n$ robot position control  using wall friction.
}
\end{figure}
